### 2022-04-23 Paper.tex
Add reference section into table of contents
Refactor abstract part

    \textbf{ABSTRACT} \emph{(in English)}

    \emph{150 -- 200 words}. \emph{An abstract is a brief statement of the
    problem or the purpose of the research. It should indicate the
    theoretical work or experimental plan used, summarize principal findings
    of the research, and point out major conclusions. Appropriate safety
    information should be included when applicable. This should be the
    section you write last to be sure that it accurately reflects the
    content of the document.}

    \textbf{ABSTRACT} \emph{(in Chinese)}

    150 - 200

@@

    \bibliographystyle{IEEEbib}
    \bibliography{Odyssey2022_BibEntries}

>>>>

    \input{abstract.tex}

@@

        \bibliographystyle{IEEEbib}
        \bibliography{reference}
        \addcontentsline{toc}{section}{References}
    \end{spacing}
